### 2017-01-27 manuscript.rmd
adds minor fix

	# Files priduced by KMRR Rscript.R with Tau values and other expression statistics
	expression_file_names = c(
		"ChickenBrawandTScomparisonTable_9_6chPC.txt", 
		"ChimpBrawandTScomparisonTable_9_6cmPC.txt", 
		"GorillaBrawandTScomparisonTable_9_6gPC.txt", 
		"HumBrawandTScomparisonTable_9_6hPC.txt", 
		"MacacaBrawandTScomparisonTable_9_6mcPC.txt", 
		"MusBrawandTScomparisonTable_9_6mPC.txt", 
		"OpossumBrawandTScomparisonTable_9_6oPC.txt", 
		"PlatypusBrawandTScomparisonTable_9_6pPC.txt"
	)

>>>>

	# Files produced by KMRR Rscript.R with Tau values and other expression statistics
	expression_file_names = c(
		"ChickenBrawandTScomparisonTable_9_6chPC.txt", 
		"ChimpBrawandTScomparisonTable_9_6cmPC.txt", 
		"GorillaBrawandTScomparisonTable_9_6gPC.txt", 
		"HumBrawandTScomparisonTable_9_6hPC.txt", 
		"MacacaBrawandTScomparisonTable_9_6mcPC.txt", 
		"MusBrawandTScomparisonTable_9_6mPC.txt", 
		"OpossumBrawandTScomparisonTable_9_6oPC.txt", 
		"PlatypusBrawandTScomparisonTable_9_6pPC.txt"
	)
